Northern Andes plant species IUCN data

### 2023-03-23 code/L0/L0_Ecuador_plants_IUCN.Rmd
updated with new IUCN link

# Read in IUCN data
Data was obtained from https://www.iucnredlist.org/search?dl=true&permalink=bd0e6db7-6fb0-4ad3-ad6c-63da82cc0999
```{r}
assessments <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/assessments.csv"))
common_names <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/common_names.csv"))
conservation_needed <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/conservation_needed.csv"))
countries <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/countries.csv"))
credits <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/credits.csv"))
dois <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/dois.csv"))
fao <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/fao.csv"))
habitats <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/habitats.csv"))
plant_specific <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/plant_specific.csv"))
references <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/references.csv"))
research_needed <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/research_needed.csv"))
simple_summary <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/simple_summary.csv"))
synonyms <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/synonyms.csv"))
taxonomy <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/taxonomy.csv"))
threats <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/threats.csv"))
usetrade <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/usetrade.csv"))
points_data <- read.csv(file.path(data_path,"IUCN/Northern Andes 3 - Range data Points/points_data.csv"))
```

>>>>

# Read in IUCN data
Data was obtained from https://www.iucnredlist.org/search?dl=true&permalink=a44f4942-2b56-47b9-8122-9896ac4af647
```{r}
assessments <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/assessments.csv"))
common_names <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/common_names.csv"))
conservation_needed <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/conservation_needed.csv"))
countries <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/countries.csv"))
credits <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/credits.csv"))
dois <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/dois.csv"))
fao <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/fao.csv"))
habitats <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/habitats.csv"))
plant_specific <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/plant_specific.csv"))
references <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/references.csv"))
research_needed <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/research_needed.csv"))
simple_summary <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/simple_summary.csv"))
synonyms <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/synonyms.csv"))
taxonomy <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/taxonomy.csv"))
threats <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/threats.csv"))
usetrade <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/usetrade.csv"))
points_data <- read.csv(file.path(data_path,"IUCN/Northern Andes 3 - Range data Points/points_data.csv"))
```
